Climate indicators

### 2023-03-07 DRAFT_climate_indicators.Rmd
Add review changes on DRAFT_climate_indicators.Rmd

@@

```{r, fig.cap="Table explaining the available climate parameters in the data set."}
senorgelayers <- read_delim("data/senorgelayers.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
DT::datatable(senorgelayers)
```

@@

```{r, fig.cap="Showing the example account area delineation (raster format)"}
dummy_aa <- x %>%
  filter(time == oldTime[1]) %>%
  adrop() %>%
  mutate(accuntingAreas = rep(c(1,2), each=length(Attribute_A)/2)) %>%
  select(accuntingAreas)

@@

```{r}
summer_median_temp <- read_stars("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/climate_indicators/aggregated_climate_time_series/summer_median_temp.tiff",
                                 proxy=F)
# This is too slow:
# readRDS("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/climate_indicators/dummy_data/summer_median_temp.rds")
# but it could be that RData works better 
```

@@

```{r, eval=T, include=F}
summer_median_temp_ref <- readRDS("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/climate_indicators/aggregated_climate_time_series/summer_median_temp_ref.RData")
```

@@

```{r, include=FALSE}
y_var_norm <- readRDS("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/climate_indicators/aggregated_climate_time_series/summer_median_temp_normalised.RData")
```

@@

```{r}
regional_means
```

>>>>

<hl/>

@@

```{r,warning=FALSE, message=FALSE, fig.cap="Table explaining the available climate parameters in the data set."}
senorgelayers <- read_delim("data/senorgelayers.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
DT::datatable(senorgelayers)
```

@@

```{r, fig.cap="Showing the example account area delineation (raster format)"}
dummy_aa <- x %>%
  filter(time == oldTime[1]) %>%
  adrop() %>%
  mutate(accountingAreas = rep(c(1,2), each=length(Attribute_A)/2)) %>%
  select(accountingAreas)

@@

```{r}
summer_median_temp <- read_stars("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/climate_indicators/aggregated_climate_time_series/temp_median_summer.tiff",
                                 proxy=F)
# This is too slow:
# readRDS("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/climate_indicators/dummy_data/summer_median_temp.rds")
# but it could be that RData works better 
```

@@

```{r, eval=T, include=F}
summer_median_temp_ref <- readRDS("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/climate_indicators/aggregated_climate_time_series/temp_median_summer_ref.RData")
```

@@

```{r, include=FALSE}
y_var_norm <- readRDS("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/climate_indicators/aggregated_climate_time_series/temp_median_summer_normalised.RData")
```

@@
